\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{pbox}
\usepackage{graphicx}
\usepackage{booktabs} % Top and bottom rules for table
\usepackage{amsfonts, amsmath, amsthm, amssymb}
\usepackage{longtable,array,color,xcolor}
\usepackage[colorlinks = true,
            urlcolor  = blue]{hyperref}

\newcommand\narrowstyle{\SetTracking{encoding=*}{-50}\lsstyle}

\pagestyle{empty}

%\usepackage[top=.6in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}

\setlength{\parindent}{0pt}
%\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\setlist{noitemsep}
%\setlist[enumerate]{topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex}

\begin{document}
{\bf \large Math 320 -- Computer Methods in the Mathematical Sciences I.}\\

\vspace{3mm}

{\bf \large Project Title:} Linear Programming: The Simplex Method and Beyond.\\
\vspace{2mm}

{\bf \large Authors:} Rohan Saraogi and Mihir Trivedi\\

\vspace{3mm}

\section{Presentation}
{\bf \large Comments:}
\begin{itemize}
\item Good examples.
\item Nice intuition provided for maximizing at vertices using
the graphical method.
\item The ``proof strategy'' display was very nice.
\item The explanation of how the simplex method worked was a bit unclear.
\item The description of Karmarkar's algorithm was (understandably) rushed.
\item The presentation was too long -- time should have been strategized.
\end{itemize}

{\bf \large Grade:} 8.5/10

A very nice presentation of a difficult topic. The talk was not
quite aimed at the audience, and there were issues with timing.
Still, a very engaging and sophisticated talk.

\section{Paper}

{\bf \large Comments:}
\begin{itemize}
\item Nicely organized into sections.
\item Some typos scattered throughout.
\item Very nicely done examples of transforming the simplex tableau (p. 9).
\item Karmarkar Assumptions section 3.2 is a bit unclear.
\item The formulation of the iterative algorithm in Section 3.3 is very nice,
and the example is well executed. It would have been nice to see a closer
analysis of the complexity of the iterative algorithm.
\item The concluding remarks are interesting, though not quite on the same theme as the rest of the paper.
\end{itemize}

{\bf \large Grade:} 9/10

Well written paper on a difficult topic. The breadth of 
material on algorithms for linear programming was very 
impressive. The paper could have been more polished but it
represents some serious research. Well done!

\end{document}
