\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{pbox}
\usepackage{graphicx}
\usepackage{booktabs} % Top and bottom rules for table
\usepackage{amsfonts, amsmath, amsthm, amssymb}
\usepackage{longtable,array,color,xcolor}
\usepackage[colorlinks = true,
            urlcolor  = blue]{hyperref}

\newcommand\narrowstyle{\SetTracking{encoding=*}{-50}\lsstyle}

\pagestyle{empty}

%\usepackage[top=.6in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}

\setlength{\parindent}{0pt}
%\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\setlist{noitemsep}
%\setlist[enumerate]{topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex}

\begin{document}
{\bf \large Math 320 -- Computer Methods in the Mathematical Sciences I.}\\

\vspace{3mm}

{\bf \large Project Title:} The Mersenne Twister Algorithm\\
\vspace{2mm}

{\bf \large Author:} Ammar Elsheshtawy\\

\vspace{3mm}

\section{Presentation}
{\bf \large Comments:}
\begin{itemize}
\item Really good at motivating the topic.
\item Excellent description of true random vs. pseudorandom.
\item Nice visualization! (noise pixels)
\item The implementation was a bit hard to follow at first, so
a walkthrough of an example was a great idea.
\item Statistical tests - very good overview!
\end{itemize}

{\bf \large Grade:} 10/10

Compelling and accessible presentation on a difficult topic.
Terrific!

\section{Paper}

{\bf \large Comments:}
\begin{itemize}
\item Cool opening graphic!
\item Nice job explaining the structure at the beginning.
\item The example going through the algorithm was very helpful.
\item The description of the ``general theorem of linear recurrence''
was a bit shortchanged -- it would be helpful to explain the connection
to linear algebra.
\item Description and commenting of the code is fantastic!
\item Interesting pros and cons section.
\end{itemize}

{\bf \large Grade:} 10/10

Very clear exposition of an interesting and challenging topic.
Well done!



\end{document}
