\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{pbox}
\usepackage{graphicx}
\usepackage{booktabs} % Top and bottom rules for table
\usepackage{amsfonts, amsmath, amsthm, amssymb}
\usepackage{longtable,array,color,xcolor}
\usepackage[colorlinks = true,
            urlcolor  = blue]{hyperref}

\newcommand\narrowstyle{\SetTracking{encoding=*}{-50}\lsstyle}

\pagestyle{empty}

%\usepackage[top=.6in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}

\setlength{\parindent}{0pt}
%\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\setlist{noitemsep}
%\setlist[enumerate]{topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex}

\begin{document}
{\bf \large Math 320 -- Computer Methods in the Mathematical Sciences I.}\\

\vspace{3mm}

{\bf \large Project Title:} Investigating Copy Number Variation in Very-Early-Onset Inflammatory Bowel Disease Using CNV Workshop\\
\vspace{2mm}

{\bf \large Authors:} Edward Zhao\\

\vspace{3mm}

\section{Presentation}
{\bf \large Comments:}
\begin{itemize}
\item Nice anatomical images for illustration.
\item Good job explaining the connection between copy number
and intensity via genotype.
\item Binary segmentation algorithm was a bit confusing to follow.
\item The permuations bit was also a bit unclear, but you did a 
good job explaining it when asked.
\end{itemize}

{\bf \large Grade:} 9/10

Really interesting presentation on a fascinating topic. Clearer
exposition of the underlying math would have made it perfect.
\section{Paper}

{\bf \large Comments:}
\begin{itemize}
\item Very nice job explaining the scientific background.
\item The statistical tools you explore in pages 5-7
are very sophististicated; it would have benefited from some explicit
tiny examples.
\item Great job explaining the linear binary segmentation, then
following up to the circular binary segmentation. Made it much easier
to understand.
\item Nice idea to compare with another software package (PennCNV) that
studies the same problems with different strategies.
\end{itemize}

{\bf \large Grade:} 9.5/10

A very sophisticated look at an interesting tool. Some
more attention to structure and exposition would have made the
paper even better.

\end{document}
