\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{pbox}
\usepackage{graphicx}
\usepackage{booktabs} % Top and bottom rules for table
\usepackage{amsfonts, amsmath, amsthm, amssymb}
\usepackage{longtable,array,color,xcolor}
\usepackage[colorlinks = true,
            urlcolor  = blue]{hyperref}

\newcommand\narrowstyle{\SetTracking{encoding=*}{-50}\lsstyle}

\pagestyle{empty}

%\usepackage[top=.6in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}

\setlength{\parindent}{0pt}
%\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\setlist{noitemsep}
%\setlist[enumerate]{topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex}

\begin{document}
{\bf \large Math 320 -- Computer Methods in the Mathematical Sciences I.}\\

\vspace{3mm}

{\bf \large Project Title:} Report on ``Accounting for Technical Noise
in Single-Cell mRNA-Seq Experiments.''\\
\vspace{2mm}

{\bf \large Authors:} Jack Norleans and Yutong (Yolanda) Wang\\

\vspace{3mm}

\section{Presentation}
{\bf \large Comments:}
\begin{itemize}
\item Nice visual aids for DNA/RNA story.
\item Really nice description of the technical problem that you're facing.
\item Size factor vs. size coeffficient was a bit confusing.
\item Good job defining a Poisson process!
\item Great job balancing the technical description with equations and formulae.
\end{itemize}

{\bf \large Grade:} 9.5

Great presentation about a very difficult paper.
Some of the mathematics was a bit confusing to follow, but overall
very accessible.

\section{Paper}

{\bf \large Comments:}
\begin{itemize}
\item Nice job laying out the steps in the algorithm.
\item Really good intuition provided throughout.
\item Well done working through all of the calculations in a clear way.
\item The hypotheses of the chi-squared test are very nicely stated.
\item Thanks for explaining your contributions.
\end{itemize}

{\bf \large Grade:} 10

Very clear and insightful exposition of a difficult paper.
Well done!

\end{document}
