\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{pbox}
\usepackage{graphicx}
\usepackage{booktabs} % Top and bottom rules for table
\usepackage{amsfonts, amsmath, amsthm, amssymb}
\usepackage{longtable,array,color,xcolor}
\usepackage[colorlinks = true,
            urlcolor  = blue]{hyperref}

\newcommand\narrowstyle{\SetTracking{encoding=*}{-50}\lsstyle}

\pagestyle{empty}

%\usepackage[top=.6in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}

\setlength{\parindent}{0pt}
%\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\setlist{noitemsep}
%\setlist[enumerate]{topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex}

\begin{document}
{\bf \large Math 320 -- Computer Methods in the Mathematical Sciences I.}\\

\vspace{3mm}

{\bf \large Project Title:} Program Termination Analysis and Cycle Detection. \\
\vspace{2mm}

{\bf \large Authors:} Lauren Leung\\

\vspace{3mm}

\section{Presentation}
{\bf \large Comments:}
\begin{itemize}
\item Nice intuition in describing decidable, (un)recognizable; nice clear
definitions.
\item Really nice description of the proof for undecidability!
\item Great idea including cute animals!
\item Good job with the Facebook applications.
\item Turtle-har really beautifully explained.
\item Good job connecting everything thematically.
\end{itemize}

{\bf \large Grade:} 10/10

Excellent presentation on an interesting topic. You were 
able to be both accessible and sophisticated. Well done!

\section{Paper}

{\bf \large Comments:}
\begin{itemize}
\item Very nice introduction, with good toy code.
\item I like the proof of undecidability (minus some typos).
\item Nice job spelling out definitions.
\item Good image + illustration of Floyd's algorithm.
\item Code is really well commented!
\item Well done including the complexity discussion -- I think the
complexity in the general directed graph case is lower than you say.
If you assume every sequence is legitimate then you will run into cycles
in the other part!
\end{itemize}

{\bf \large Grade:} 9.5/10

Very nicely written paper that tackles the theoretical and
computational aspects of the problem ambitiously. It could have
been a bit more polished (content-wise and formatting-wise), but
overall great job!



\end{document}
