\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{pbox}
\usepackage{graphicx}
\usepackage{booktabs} % Top and bottom rules for table
\usepackage{amsfonts, amsmath, amsthm, amssymb}
\usepackage{longtable,array,color,xcolor}
\usepackage[colorlinks = true,
            urlcolor  = blue]{hyperref}

\newcommand\narrowstyle{\SetTracking{encoding=*}{-50}\lsstyle}

\pagestyle{empty}

%\usepackage[top=.6in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}

\setlength{\parindent}{0pt}
%\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\setlist{noitemsep}
%\setlist[enumerate]{topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex}

\begin{document}
{\bf \large Math 320 -- Computer Methods in the Mathematical Sciences I.}\\

\vspace{3mm}

{\bf \large Project Title:} Game Theory and Applications\\
\vspace{2mm}

{\bf \large Authors:} Robert Maura and Natalie Weiss\\

\vspace{3mm}

\section{Presentation}
{\bf \large Comments:}
\begin{itemize}
\item Nice outline. Good formal definitions.
\item Well-explained examples. Nice prisoner clip art!
\item The relationship between actions and payoffs could have been
better explained.
\item Funny \& Well thought out discussion of complexity.
\item Good analogy for diminishing returns.
\item Great explanation for the pieces of the utility function.
\item Cool Monte Carlo illustrations -- would have been nice to see
how the code for this was executed.
\end{itemize}

{\bf \large Grade:} 9.5/10

There were a few areas where the exposition could have been improved.
Still it was an excellent presentation that gave the audience a nice
introduction to your topic.

\section{Paper}

{\bf \large Comments:}
\begin{itemize}
\item Nice job outlining the paper in the introduction!
\item Formatting in LaTeX makes the paper really easy to read.
\item Definition 2.7 -- titled ``Non-zero sum game'' but it defined a zero-sum game.
\item Code is very nicely commented.
\item Nice sense of humor :-P
\item The difference between payoff and utility is not so clear in your
exposition -- is it that payoff is objective and utility is subjective?
Or is it that the utility depends on other people's payoffs?
\item The Monte carlo simulations are nicely explained and the displays are
thought-provoking.
\end{itemize}

{\bf \large Grade:} 9.5/10

Very nice balance of new theory, computational aspects, and 
exposition. It could have been a bit more polished, but all in all
a great paper!




\end{document}
