\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{pbox}
\usepackage{graphicx}
\usepackage{booktabs} % Top and bottom rules for table
\usepackage{amsfonts, amsmath, amsthm, amssymb}
\usepackage{longtable,array,color,xcolor}
\usepackage[colorlinks = true,
            urlcolor  = blue]{hyperref}

\newcommand\narrowstyle{\SetTracking{encoding=*}{-50}\lsstyle}

\pagestyle{empty}

%\usepackage[top=.6in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}

\setlength{\parindent}{0pt}
%\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\setlist{noitemsep}
%\setlist[enumerate]{topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex}

\begin{document}
{\bf \large Math 320 -- Computer Methods in the Mathematical Sciences I.}\\

\vspace{3mm}

{\bf \large Project Title:} Extraction of Brain Tumors from MRI Scans\\
\vspace{2mm}

{\bf \large Authors:} Varun S. Rajagopal\\

\vspace{3mm}

\section{Presentation}
{\bf \large Comments:}
\begin{itemize}
\item Very good justification of your work, and why you're doing it.
\item Very nice demonstration of convolution filter.
\item Great job incorporating code into the talk.
\item Great examples for all your filters.
\item Beautiful images throughout.
\item Nice idea to implement it on a random Google search photo!
\end{itemize}

{\bf \large Grade:} 10/10

Terrific presentation of a sophisticated and well-motivated topic.

\section{Paper}

{\bf \large Comments:}
\begin{itemize}
\item It would be interesting to hear details about how you modified
the method from Patil-Balchandra.
\item Nice job citing throughout.
\item Good example convolution.
\item Nice explanation of effects of high-pass and median filtering.
\item Explanation of watershed transform is a bit unclear.
\item Your paper does an excellent job of citing relevant bits of code
in the text of the paper, then reporting the full (well-commented) code
at the end.
\end{itemize}

{\bf \large Grade:} 10/10

A computationally and mathematically sophisticated account of image
processing with a great application. Excellent job!


\end{document}
